Approximation as Differentiation

### 2025-05-04 appendix/notes/auto-diff.tex
Move auto-diff to after definition of FinVect.

Write $\tangents_x(\RR^n)$ for the tangent space at a point $x \in \RR^n$. Then the \emph{forward derivative}
(tangent map or pushforward) $\pushf{f}_x$ of a differentiable function $f: \RR^m \to \RR^n$ at $x \in
\RR^m$ is a linear map $\tangents_x(\RR^m) \linearto \tangents_{f(x)}(\RR^n)$. Because $\RR^n$ is a Euclidean
manifold, $\tangents_x(\RR^n)$ is naturally isomorphic to $\RR^n$, so actually $\pushf{f}_x: \RR^m \linearto
\RR^n$. The \emph{backward derivative} (cotangent map or pullback) $\pullf{f}_x$  is a linear map $\RR^n
\linearto \RR^m$.

@@

>>>>

Write $\tangents_x(\RR^n)$ for the tangent space at a point $x \in \RR^n$. Then the \emph{forward derivative}
(tangent map or pushforward) $\pushf{f}_x$ of a differentiable function $f: \RR^m \to \RR^n$ at $x \in \RR^m$
is a linear map $\tangents_x(\RR^m) \linearto \tangents_{f(x)}(\RR^n)$. Because $\RR^n$ is Euclidean (flat),
$\tangents_x(\RR^n)$ is naturally isomorphic to $\RR^n$, so actually $\pushf{f}_x: \RR^m \linearto \RR^n$. The
\emph{backward derivative} (cotangent map or pullback) $\pullf{f}_x$  is a linear map $\RR^n \linearto \RR^m$.

@@

\subsubsection{Automatic differentiation via the Grothendieck construction}
